### 2018-09-17 source/Ch2-techniques/RIME.tex
added patrick charlot things

\pg
This gives us an elegant formulation of the relationship between the signal emitted by an astrophysical source and its corresponding measured visibility. The Stokes parameters of our source can be directly calculated from our measured visibility, provided $\Jones_p$ and $\Jones_q$ are known. Of course, in practice, they are not, and must therefore be modelled. To do this, we must expand each Jones matrix into a corresponding Jones chain.

>>>>

\pg
This gives us an elegant formulation of the relationship between the signal emitted by an astrophysical source and its corresponding measured visibility. The Stokes parameters\footnote{Stokes parameters determine the polarisation of light; we will not get into more details in this manuscript, as it is hardly relevant to the topic at hand. Suffice to say that the 2-vector formalism helps account for the polarised nature of light.} of our source can be directly calculated from our measured visibility, provided $\Jones_p$ and $\Jones_q$ are known. Of course, in practice, they are not, and must therefore be modelled. To do this, we must expand each Jones matrix into a corresponding Jones chain.

### 2018-09-17 source/Ch2-techniques/lofar.tex
added patrick charlot things

\pg
We see the presence, in both cases, of two very different antenna types. One of these antenna types is not a single antenna, but rather a phased array: 16 antenna dipoles distributed in a $4 \times 4$ array. International LOFAR stations include 96 such tiles, distributed in a ``filled-disk" pattern, where the disk fill ratio is determined by the size of the tile. Dutch ``remote" stations have 48 such tiles spread into 2 disks (HBA\textunderscore INNER and HBA\textunderscore OUTER), while ``core" station HBA tiles are split into two 24-tile crosses. This pattern is shown in \cref{fig.hba.tile}. The antennas from each tile are combined into a phased array with a single ``tile beam", and all tile beams are themselves combined as a phased array into a station beam\footnote{Reference: \href{https://www.astron.nl/radio-observatory/astronomers/technical-information/antennae/antennae-description}{ASTRON technical description}: \url{https://www.astron.nl/radio-observatory/astronomers/technical-information/antennae/antennae-description}}.% This station beam is then pointed digitally.
\begin{figure}[h!]
\includegraphics[width=0.45\textwidth]{images/{Schematic-diagram-of-a-24-tile-LOFAR-HBA-station-A-tile-is-made-of-16-dual-polarization.png}}
\caption{\label{fig.hba.tile} Layout of a single HBA tile. Source: \href{https://www.researchgate.net/profile/Sarod_Yatawatta/publication/281316394/figure/fig1/AS:614002589720576@1523401033149/Schematic-diagram-of-a-24-tile-LOFAR-HBA-station-A-tile-is-made-of-16-dual-polarization.png}{Sarod Yatawatta researchgate profile}}
\end{figure}

>>>>

\pg
We see the presence, in both cases, of two very different antenna types. One of these antenna types is not a single antenna, but rather a phased array: 16 antenna dipoles distributed in a $4 \times 4$ array. International LOFAR stations include 96 such tiles, distributed in a ``filled-disk" pattern, where the disk fill ratio is determined by the size of the tile. Dutch ``remote" stations have 48 such tiles spread into 2 disks (HBA\textunderscore INNER and HBA\textunderscore OUTER), while ``core" station HBA tiles are split into two 24-tile crosses. This pattern is shown in \cref{fig.hba.tile}. The antennas from each tile are combined into a phased array with a single ``tile beam", and all tile beams are themselves combined as a phased array into a station beam\footnote{Reference: \href{https://www.astron.nl/radio-observatory/astronomers/technical-information/antennae/antennae-description}{ASTRON technical description}: \url{https://www.astron.nl/radio-observatory/astronomers/technical-information/antennae/antennae-description}}.% This station beam is then pointed digitally.
\begin{figure}[h!]
\begin{subfigure}{.45\textwidth}
	\centering
	\includegraphics[width=0.95\textwidth]{images/{Schematic-diagram-of-a-24-tile-LOFAR-HBA-station-A-tile-is-made-of-16-dual-polarization.png}}
	\caption{\label{fig.hba.tile} Layout of a single HBA tile. Source: \href{https://www.researchgate.net/profile/Sarod_Yatawatta/publication/281316394/figure/fig1/AS:614002589720576@1523401033149/Schematic-diagram-of-a-24-tile-LOFAR-HBA-station-A-tile-is-made-of-16-dual-polarization.png}{Sarod Yatawatta researchgate profile}}
\end{subfigure}
\begin{subfigure}{.45\textwidth}
	\centering
	\includegraphics[width=0.95\textwidth]{images/{hbaim.jpeg}}
	\caption{\label{fig.hba.im} Picture of an HBA tile. Source: Figure 1 of \citetads{2012A&A...545A.108N}}
\end{subfigure}
\caption{HBA tile layout and image. Note that both cases show a 24-tile HBA array: each core station includes two such arrays. International stations include a single larger tile array.}
\end{figure}

### 2018-09-17 source/Ch2-techniques/science.tex
added patrick charlot things

\pg
The synchrotron power spectrum of a population of electrons with exactly the same energy is a function of its Lorentz factor and its emission angle\footnote{The emission angle is the angle between the electron's total velocity (including z-axis) and its radial velocity.} \citepads{1994hea2.book.....L}. The typical radiation spectrum for a single electron is shown in \cref{fig.synchrotron.1electrion} as a function of the critical frequency, which is itself a function of the emission angle, the Lorentz factor and the magnetic field strength: $\nu_c=3/2\frac{\gamma^2 e B}{2\pi m_e c}\sin(\theta)$.
$\nu_c=3/2\frac{\gamma^2 e B}{2\pi m_e c}\sin(\theta)$.
\begin{figure}[!h]
\centering
\includegraphics[width=0.9\textwidth]{images/Synchrotron-single-electron.png}
\caption{\label{fig.synchrotron.1electrion} Characteristic spectrum of synchrotron emission for a population of single-energy electrons. Arbitrary unit scale. Source: NRAO online course: \url{https://www.cv.nrao.edu/~sransom/web/Ch5.html}}
\end{figure}

>>>>

\pg
The synchrotron power spectrum of a population of electrons with exactly the same energy is a function of its Lorentz factor and its emission angle\footnote{The emission angle is the angle between the electron's total velocity (including z-axis) and its radial velocity.} \citepads{1994hea2.book.....L}. The typical radiation spectrum for a single electron is shown in \cref{fig.synchrotron.1electrion} as a function of the critical frequency, which is itself a function of the emission angle $\theta$, the Lorentz factor $\gamma$ and the magnetic field strength $B$: $\nu_c=3/2\frac{\gamma^2 e B}{2\pi m_e c}\sin(\theta)$. $e$ and $m_e$ are the electron charge and mass, respectively.
%$\nu_c=3/2\frac{\gamma^2 e B}{2\pi m_e c}\sin(\theta)$.
\begin{figure}[!h]
\centering
\includegraphics[width=0.9\textwidth]{images/Synchrotron-single-electron.png}
\caption{\label{fig.synchrotron.1electrion} Characteristic spectrum of synchrotron emission for a population of single-energy electrons. Arbitrary unit scale. Source: NRAO online course: \url{https://www.cv.nrao.edu/~sransom/web/Ch5.html}}
\end{figure}
